---
title: "Preliminary"
author: "Irvin Rojas and Jisang Yu"
date: "5/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

## Data summary
* (I don't really know how to make a summary table... so here is the ugly one)
```{r prep, results="hide"}
#libraries
library(tidyverse)
library(foreign)
library(lmtest)

#read data
data<-read.dta("cleaned_v1.dta") 
```

```{r prep2, collectcode=TRUE}
data %>%
  summarise(
          count = n(),
          mean_d_wage = mean(d_mhrwageactive, na.rm = TRUE),
          sd_d_wage = sd(d_mhrwageactive, na.rm = TRUE),
          mean_w_covid_apr = mean(w_covid_apr, na.rm = TRUE),
          sd_w_covid_apr = sd(w_covid_apr, na.rm = TRUE))
```

## Preliminary regressions

* First, let's assess whether the Covid exposure of the Mexican migrants in US has any impacts on the local wages ($W$) in the Mexican cities
$$
\Delta W_{c}=\alpha+\beta \sum_{s} \theta_{sc}Covid_s+\varepsilon_c
$$
where
$$
\Delta W_{c}=W_{c,2020q4}-W_{c,2019q4}
$$
$$
\theta_{sc}=\frac{\text{Number of travelers from city $c$ to state $s$}}{\text{Total number of travels from city $c$}}
$$
and $Covid_s$ is the number of cases in state $s$ (per million people).
```{r prelim, collectcode=TRUE}
#regression
reg1<-lm(d_mhrwageactive~w_covid_apr, data=data)
coeftest(reg1)
```

* Second, let's assess whether there are differential effects between agricultural and non-agricultural sectors:
$$
\Delta W_{c}=\alpha+\beta_1 \sum_{s} \theta_{sc}Covid_s +\beta_2 \sum_{s} \theta_{sc} Ag_s Covid_s +\varepsilon_c
$$
where $Ag_s$ is the share of Mexican-born agricultural workers over total agricultural workers in state $s$.
```{r prelim2, collectcode=TRUE}
#regression2
reg2<-lm(d_mhrwageactive~w_covid_apr+w_covid_apr_ag, data=data)
coeftest(reg2)
```

## Considerations
* Small sample: Number of cities=37
* Other sectors?
* Mexico local Covid exposure?
* Control for the importance of the migration in city $c$?
